---
format: 
  html:
    toc: true
    toc-location: left
    embed-resources: true
    grid:
      sidebar-width: 200px
      body-width: 1200px
      margin-width: 100px
editor: source
params:
  iso3c: "NULL"
  country: "NULL"
  admin_level: "NULL"
  version: "NULL"
  n_sites: "NULL"
---

```{css, echo = FALSE}
.output {
max-height: 500px;
overflow-y: auto;
max-width: 1000px
}
```

```{r}
#| echo: false
#| warning: false
plots <- readRDS("calibration_plots.rds")

title <- paste0(
  "Calibration report. ",
  params$country, " (", params$iso3c, ").",
  " Admin level: ", params$admin_level, ".",
  " Version: ", params$version
)
facet_plot_width <- 10
```

---
title: "`r title`"
title-block-banner: true
---

Calibration is performed to be match prevalence in the period 2014:2018.
Prevalence estimates are from the Malaria Atlas Project rasters, aggregated using
our spatial boundaries and estimates of population at risk where necessary.


## National summaries

::: panel-tabset

## PfPr (MAP)

```{r plot-pf-prev}
#| echo: false
#| warning: false
plots$national_prev_pf_plot
```

## PvPr (MAP)

```{r plot-pv-prev}
#| echo: false
#| warning: false
plots$national_prev_pv_plot
```

## Clinical incidence (WMR)

```{r plot-incidence}
#| echo: false
#| warning: false
plots$national_inc_plot
```

## Cases (WMR)

```{r plot-cases}
#| echo: false
#| warning: false
plots$national_cases_plot
```

## Mortality Rate (WMR)

```{r plot-mortality}
#| echo: false
#| warning: false
plots$national_mortality_plot
```

## Deaths (WMR)

```{r plot-deaths}
#| echo: false
#| warning: false
plots$national_deaths
```
:::


### Calibration Pf

```{r,echo=FALSE}
fheight_prev = min(params$n_sites, 650)
```

```{r plot-pf_calibration, fig.height=fheight_prev}
#| class: output
#| echo: false
#| warning: false
plots$calibration_fit_pf
```

### Calibration Pv

```{r plot-pv_calibration, fig.height=fheight_prev}
#| class: output
#| echo: false
#| warning: false
plots$calibration_fit_pv
```

