---
format: 
  html:
    toc: true
    toc-location: left
    embed-resources: true
editor: visual
params:
  iso3c: "NULL"
  country: "NULL"
  version: "NULL"
---

## Site file summary for `r params$country`, version: `r params$version`

``` {r}
#| echo: false
plots <- readRDS("diagnostic_plots.RDS")
```

## World malaria report burden estimates

::: {.panel-tabset}
## Clinical incidence

``` {r}
#| echo: false
plots$incidence
```

## Cases

``` {r}
#| echo: false
plots$cases
```

## Mortality Rate

``` {r}
#| echo: false
plots$mortality
```

## Deaths

``` {r}
#| echo: false
plots$deaths
```

:::

## Malaria Atlas Project prevalence summaries

::: {.panel-tabset}
## Prevalence

``` {r}
#| echo: false
plots$country_prevalence
```

## PfPr Map

``` {r}
#| echo: false
plots$pfpr_map
```

## PvPr Map

``` {r}
#| echo: false
plots$pvpr_map
```

:::

## Population estimates

::: {.panel-tabset}
## Population

``` {r}
#| echo: false
plots$country_population
```

## Population at risk
``` {r}
#| echo: false
plots$country_par
```

## Urban/Rural population
``` {r}
#| echo: false
plots$country_urban_rural
```

## Proportion Urban
``` {r}
#| echo: false
plots$country_prop_urban
```

## Urban/Rural subnational population
``` {r}
#| echo: false
plots$area_urban_rural
```

:::

## Age-distribution
``` {r}
#| echo: false
plots$age_dist
```