---
format: 
  html:
    toc: true
    toc-location: left
    embed-resources: true
    grid:
      sidebar-width: 200px
      body-width: 1200px
      margin-width: 100px
editor: source
params:
  iso3c: "NULL"
  country: "NULL"
  admin_level: "NULL"
  boundary: "NULL"
---

```{css, echo = FALSE}
.output {
max-height: 500px;
overflow-y: auto;
max-width: 1000px
}
```

```{r}
#| echo: false
#| warning: false
plots <- readRDS("diagnostic_plots.RDS")
library(patchwork)
title <- paste0(
  params$country, " (", params$iso3c, ").",
  " Admin level: ", params$admin_level, ".",
  " Boundary: ", params$boundary
)
facet_plot_width <- 10
```

---
title: "`r title`"
title-block-banner: true
---

## Subnational units

```{r,echo=FALSE}
n_facets <- length(plots$geom_graphic_areas$layers[[1]]$data$name)
ncols <- plots$geom_graphic_areas$facet$params$ncol
nrows <- ceiling(n_facets / ncols)
fheight_units <- (facet_plot_width / ncols) * nrows
```

```{r plot-geo-areas, fig.height=fheight_units, fig.width=facet_plot_width}
#| class: output
#| echo: false
plots$geom_graphic_areas
```

## World malaria report burden estimates

::: panel-tabset
## Clinical incidence

```{r plot-incidence}
#| echo: false
plots$incidence
```

## Cases

```{r plot-cases}
#| echo: false
plots$cases
```

## Mortality Rate

```{r plot-mortality}
#| echo: false
plots$mortality
```

## Deaths

```{r plot-deaths}
#| echo: false
plots$deaths
```
:::

## Malaria Atlas Project prevalence summaries

### Prevalance timeseries

```{r plot-prevalence-timeseries}
#| echo: false
#| warning: false
plots$country_prevalence
```

### Prevalence maps

```{r,echo=FALSE}
fheight_prev = min(length(unique(plots$pfpr_map$data$year)) * 2, 650)
```

```{r plot-prevalence-maps, fig.height=fheight_prev}
#| class: output
#| echo: false
(plots$pfpr_map | plots$pvpr_map)
```

## Population and Demography

### Population timeseries

::: panel-tabset
## Population

```{r plot-population}
#| echo: false
plots$country_population
```

## Population at risk

```{r plot-population-at-risk}
#| echo: false
plots$country_par
```

## Urban/Rural population

```{r plot-urban-rural-population}
#| echo: false
plots$country_urban_rural
```

## Proportion Urban

```{r plot-proportion-urban}
#| echo: false
plots$country_prop_urban
```

:::

### Subnational population at risk
```{r,echo=FALSE}
n_facets <- length(unique(plots$area_par$data$name))
ncols <- plots$area_par$facet$params$ncol
nrows <- ceiling(n_facets / ncols)
fheight_area_par <- (facet_plot_width / ncols) * nrows
```

```{r plot-par-subnational, fig.height=fheight_area_par, fig.width=facet_plot_width}
#| class: output
#| echo: false
plots$area_par
```


### Urban/Rural subnational population
```{r,echo=FALSE}
n_facets <- length(unique(plots$area_urban_rural$data$name))
ncols <- plots$area_urban_rural$facet$params$ncol
nrows <- ceiling(n_facets / ncols)
fheight_urban <- (facet_plot_width / ncols) * nrows
```

```{r plot-urban-rural-subnational, fig.height=fheight_urban, fig.width=facet_plot_width}
#| class: output
#| echo: false
plots$area_urban_rural
```

### Age-distribution

```{r,echo=FALSE}
n_facets <- length(unique(plots$age_dist$data$year))
ncols <- plots$age_dist$facet$params$ncol
nrows <- ceiling(n_facets / ncols)
fheight_age <- (facet_plot_width / ncols) * nrows
```

```{r plot-age-dist, fig.height=fheight_age, fig.width=facet_plot_width}
#| class: output
#| echo: false
plots$age_dist
```

## Interventions 
```{r plot-interventions}
#| echo: false
#| warning: false
plots$interventions
```

```{r,echo=FALSE}
n_facets <- length(unique(plots$area_interventions$data$name))
nrows <- plots$area_interventions$facet$params$nrow
ncols <- ceiling(n_facets / nrows)
fheight_interventions <- (facet_plot_width / ncols) * nrows
```

```{r plot-subnational-interventions, fig.height=fheight_interventions, fig.width=facet_plot_width}
#| class: output
#| echo: false
plots$area_interventions
```

## Seasonality
```{r,echo=FALSE}
fheight_seasonality = min(length(unique(plots$rainfall$data$name)) * 2, 650)
```

```{r plot-seasonality, fig.height=fheight_seasonality}
#| class: output
#| echo: false
plots$rainfall | plots$seasonality
```

## Mosquito vectors

### Species
```{r,echo=FALSE}
fheight_vectors = min(length(unique(plots$vectors$data$name)) * 0.25, 650)
```

```{r plot-species, fig.height=fheight_vectors}
#| class: output
#| echo: false
plots$vectors
```

### Pyrethroid resistance
```{r plot-resistance}
#| echo: false
plots$resistance
```

## Blood disorders

::: panel-tabset
## GDP6

```{r plot-gpd5}
#| echo: false
plots$gdp6
```

## Sicklecell

```{r plot-sicklecell}
#| echo: false
plots$sickle
```

## Duffy negativity

```{r plot-duffy-negativity}
#| echo: false
plots$duffy
```

## HPC

```{r plot-hpc}
#| echo: false
plots$hpc
```

:::

## Accessibility

::: panel-tabset
## Motor transport

```{r plot-motor-access}
#| echo: false
plots$motor
```

## Walking

```{r plot-walking-access}
#| echo: false
plots$walk
```

## To city

```{r plot-city-access}
#| echo: false
plots$city
```


:::